A simple place to start is the *comment*. A comment is a statement that
the computer will *ignore*. It is text that we put in the program for
our benefit, to explain what is going on to a human reader.

This is an example of a comment:

```{r}
# This is a comment. It doesn't have any effect.
```

The comment starts with a hash character `#`. This character tells the
computer that the rest of the line is a comment, and therefore, that it
can ignore everything on that line that follows the `#`.



The core of the program to solve the ambulances problem above begins
with this command to the computer:



```{r}
a = sample(1:10, 12, replace=TRUE)
```

This uses the `sample` function to generate random integers (counting
numbers) from 1 through 10. The 12 in the command tells R to generate 12
of these numbers. `replace=TRUE` tells R to sample *with replacement*.

For example, the chances of getting a particular result - such as a 3 -
for the first random number - are 1 in 10, or p= 1/10 = 0.1. If we
resample *with replacement* then the chances of getting 3 in the second
number are unchanged, at p=0.1. It is as if we put 10 balls into a
bucket, numbered one through ten, and then selected 12 balls from the
bucket; but after we have selected a ball, we record the number and
*replace* it in the bucket, and shake up the bucket again.

So — the command above orders the computer to randomly generate 12
numbers between “1” and “10.” Inasmuch as each ambulance has a 1 in 10
chance of being defective, we decide arbitrarily that a “1” stands for a
defective ambulance, and the other nine numbers (from “2” to “10”) stand
for a not-defective ambulance. The command orders the computer to store
the results of the random drawing in a location in the computer’s memory
to which we give a name such as `a` or `ambulances`. When we run a
statement like the one above, `a` is a *variable* - the *name* `a`
refers to the *value*, which is the sequence of random numbers the
computer created using `sample`.

We can show the value of the variable `a` in the notebook or interactive
terminal by using the `print` function:

```{r}
print(a)
#>  [1] 7 5 6 4 6 9 5 5 8 2 7 5
```

This shows the 12 random values that we got from `sample`.

The next key element in the core of the program is:

```{r}
b = sum(a == 1)
```

This command orders the computer to count the number of “1’s” among the
12 numbers that are in location `a` following the random drawing carried
out by the `sample` operation. The result of the count will be somewhere
between 0 and 12, the number of ambulances that might be out-of-order on
a given day. The result is then placed in another location in the
computer’s memory that we label `b`.

```{r}
# Show the value of b
print(b)
#> [1] 0
```

Now let us place the commands to generate the random numbers, and count
how many 1s we get, within the entire program that we use to solve this
problem, which is:

```{r}
# Make an array that has 400 elements.
# We will use this to store the counts for our 400 repetitions
results <- numeric(400)

# Repeat the simulation 400 times
for (i in 1:400) {

    # The commands between the { above and the } below are the procedure for
    # one trial.
    # The computer runs these commands from first to last, for each trial.

    # Generate 12 numbers, each between "1" and "10," and put them in vector a.
    # Each number will represent an ambulance, and we let 1 represent
    # a defective ambulance.
    a <- sample(1:10, 12, replace=TRUE)

    # Count the number of defective ambulances, and put the result in b.
    b <- sum(a == 1)

    # Keep track of each trial's result in "results".
    results[i] <- b

    # End this trial, then go back and repeat the process until all 400 trials
    # are complete.
}

# Now we have finished the 400 trials.

# Determine how many trials resulted in more than 3 ambulances out of order.
bad_day_count <- sum(results > 3)

# Convert to a proportion.
bad_day_prop <- bad_day_count / 400

# Print the result.
print(bad_day_prop)
#> [1] 0.0275
```
